Volunteers in the Clouds: A Web Based Architecture to Harness Volunteer Resources for Low Cost Distributed Evolutionary Computation

### 2015-12-14 special-issue-ci/volunteer-clouds-ieee-ci-si.tex
Threats to vilidity
Please check

>>>>

There are several validity threats to the design of this study.
Participants of the experiments were mainly members of our 
own social networks, personal colleagues, friends 
and acquaintances, when extending this work other options 
should be considered in order to include 
a wider audience with different motives for participation.
Another threat is that participants were anonymous so the amount of repeated 
participations and the effects this had in the outcome is not
known. Another issue is that the scalability of the system was not thoroughly tested
but for the amount of participants the basic configuration 
was more than adequate, again more experiments are needed in order
to assess the capability both with more clients and other server
configurations. Although care was taken to include representative benchmarks
of real world problems, more experiments with a broader coverage 
should allow a better understanding of the practical limitations of
the architecture and the tools chosen.
